Are environmental and geographic variables effective surrogates for genetic variation in conservation planning?

### 2016-04-04 article/figures.Rmd
+ fixes to si and figures

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=genetic.held),
		data=scenario.DF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_text(aes(x=Prioritisation, y=letter.height, label=letter),
			data=scenario.PDF, position=position_dodge(0.9)) +
		geom_text(aes(x=0.6, y=1.09, label=panel.letter),
			data=scenario.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		facet_grid(Context ~ Metric)
})
```

>>>>

# make plot
suppressWarnings({
	ggplot(aes(x=Prioritisation,y=genetic.held),
		data=scenario.DF) +
		geom_boxplot(position=position_dodge(0.9)) +
		geom_text(aes(x=Prioritisation, y=letter.height, label=letter),
			data=scenario.PDF, position=position_dodge(0.9)) +
		geom_text(aes(x=0.6, y=1.09, label=panel.letter),
			data=scenario.PDF) +
		scale_fill_manual(name='Prioritisation',
			values=c('grey80','grey50','grey20')) +
		ylab('Genetic variation secured (%)') +
		xlab('') +
		scale_y_continuous(breaks=c(0,0.25,0.5,0.75,1), limits=c(NA, 1.2)) +
		theme_classic() +
		theme(strip.background = element_rect(fill='grey20'),
			strip.text = element_text(color='white'),
			panel.border = element_rect(color='black', fill=NA),
			axis.text.x=element_text(angle=45, hjust=1, vjust=1)) +
		geom_abline(intercept=intercept=rapr.params.LST[[MODE]]$surrogacy.analysis$genetic.target,
			slope=0 color='red', linetype='dashed') +
		facet_grid(Context ~ Metric)
})
```
